Contextual Combinatorial Cascading Bandits

### 2015-11-27 contextual combinatorial cascading bandits.tex

From this lemma, we can find a prefix $\bB_t$ of $\bA_t$ such that $p_{B_t}$ is large enough and $\Delta_{\bB_t}$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\bete_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$, thus for $R(T)$. We leave all details in the next subsection.

>>>>

From this lemma, we can find a prefix $\bB_t$ of $\bA_t$ such that $p_{B_t}$ is large enough and $\Delta_{\bB_t}$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{t, \bA_t}|\cH_{t-1}]$, thus for $R(T)$. We leave all details in the next subsection.
